Characterising cheque dishonour cases in India: Causes for delays and policy implications

### 2022-04-14 DOC/introduction.tex
Fixed more errors

Such knowledge is based on the assumption that cheque dishonour cases are a large burden on the judiciary and has thus focused on expediting disposal. For example, \gls{lci} (2008), by relying on newspaper reports concerning the proportion of cheque dishonour cases, recommended setting up Fast Track Magisterial Courts \autocite{lci2008_138, bhan2015_placing}. However, it did not define \textit{fast-track courts} or give guidance concerning how and where they would operate. Developing this work, DAKSH (2017) examined the behaviour of cheque dishonour cases in the Indian courts by looking at over 67000 cases. In most cases, it found that resolution is delayed well beyond statutorily prescribed timelines and that certain banks and financial institutions are frequent complainants \autocite{sridhar2017_cheque}. As per our own estimates, less than 20\% of the cases get disposed within the stimulated timeline (see Figure \ref{fig:stateSurvival} for comparison across states in India).

@@

\textbf{What we do?}: This study, based on orders of the Supreme Court and the report of the Amici Curiae, attempts to assess the effect of suggested interventions on the expeditious trial of cases under \S~138 of the \gls{ni}. First, we empirically estimate the volume of NI 138 cases differing courts. Given the disagreement, any acceptance among policymakers that \gls{ni} cases (\textit{cheque dishonour cases} hereinafter) are the reason for India's slow judiciary is likely to lead to misguided solutions. The misrepresentation could lead to diverting resources from other routes of judicial reform. Thus, one requires a more detailed analysis of the proportion of such cases, their causes, timelines, etc. This information can help judges and policymakers better target interventions.\footcite[For the importance of accurate judicial data, see][]{damle2020_ecourtsData, daksh2020_data, damle2020_land}

Second, we examines the determinants of case duration as identified by the Amici Curiae and the Supreme Court.

At last, we evaluate the effect of 2015 Amendments on the duration of cases.

\textbf{Key findings/Summary of our results}

\textbf{How we contribute to the debate?}

>>>>

Such knowledge is based on the assumption that cheque dishonour cases are a large burden on the judiciary and has thus focused on expediting disposal. For example, \gls{lci} (2008), by relying on newspaper reports concerning the proportion of cheque dishonour cases, recommended setting up Fast Track Magisterial Courts \autocite{lci2008_138, bhan2015_placing}. However, it did not define \textit{fast-track courts} or give guidance concerning how and where they would operate. Developing this work, \textcite{sridhar2017_cheque} examined the behaviour of cheque dishonour cases in the Indian courts by looking at over 67000 cases. In most cases, it found that resolution is delayed well beyond statutorily prescribed timelines and that certain banks and financial institutions are frequent complainants \autocite{sridhar2017_cheque}. As per our own estimates, less than 20\% of the cases get disposed within the stipulated timeline (see Figure \ref{fig:stateSurvival} for comparison across states in India).

@@

This study, based on orders of the Supreme Court and the report of the Amici Curiae, attempts to assess the effect of suggested interventions on the expeditious trial of cases under \S~138 of the \gls{ni}. First, we estimate the volume of NI 138 cases in the subordinate courts. Given the disagreement, any acceptance among policymakers that \gls{ni} cases (\textit{cheque dishonour cases} hereinafter) are the reason for India's slow judiciary is likely to lead to misguided solutions. The misrepresentation could lead to diverting resources from other routes of judicial reform. Thus, one requires a more detailed analysis of the proportion of such cases, their causes, timelines, etc. This information can help judges and policymakers better target interventions.\footcite[For the importance of accurate judicial data, see][]{damle2020_ecourtsData, daksh2020_data, damle2020_land}

Second, we estimate the likely impact of some select recommendations of the Amici Curiae and the Supreme Court. This can help the court gauge how effective their recommended reforms are likely to be. As we show, some of the recommendations can end up being counterproductive. We, thus, also demonstrate the need for judicial decision-making to be rooted in data.
